---
title: "Predict Epidemic Tools"
output:
  html_document:
    df_print: paged
---
## Data Tools 

```{r EpidemicDataFrameSerfling}
#' @param data data 
#' @param d1 1st epidemic week to consider
#' @param d2 last epidemic week to consider
#' @return a data frame with a year column and two columns with the rate et the deseasonalized rate for epidemic weekds d1 to d2
EpidemicDataFrameSerfling <- function(data, d1, d2) {
  sub_data <- subset(x = data, subset = epid_serfling == 1)
  season <- unique(sub_data$season)
  l.season <- length(season)
  l.epid <- d2 - d1 + 1
  epidemic_data <-
    data.frame(
      season = rep(season, each = l.epid),
      weeks = d1:d2,
      t_inc = rep(0, l.epid * length(season)),
      t_inc_cent = rep(0, l.epid * length(season))
    )
  
  for (i in season) {
    temp <- subset(sub_data, subset = season == i)
    epidemic_data[epidemic_data$season == i,]$t_inc <-
      temp[d1:d2,]$t_inc
    epidemic_data[epidemic_data$season == i,]$t_inc_cent <-
      temp[d1:d2,]$t_inc_cent
  }
  return(epidemic_data)
}
```

```{r EpidemicDataFrame}
#' @param data data 
#' @param d number of epidemic weeks to consider
#' @param thres threshold for the definition of an epidemic 
#' @return a data frame with a year column and two columns with the rate et the deseasonalized rate for the d first weeks when thres has been exceeded
EpidemicDataFrame <- function(data, d, thres) {
  sub_data <- subset(x = data, subset = epid_serfling == 1)
  season <- unique(sub_data$season)
  l.season <- length(season)
  epidemic_data <- data.frame(
    season = rep(0, d),
    weeks = 1:d,
    t_inc = rep(NA, d),
    t_inc_cent = rep(NA, d)
  )
  
  for (i in season) {
    temp <- subset(sub_data, subset = season == i)
    last.week <- length(temp$season)
    index <- which(temp$t_inc > thres)
    if (length(index) > 1) {
      first.week <- index[which(diff(index) == 1)[1]]
      toto <- temp[first.week:last.week,]
      l.toto <- length(toto$t_inc)
      if (l.toto > d) {
        epidemic_data <- rbind(epidemic_data,
                               cbind(
                                 season = rep(i, d),
                                 weeks = 1:d,
                                 t_inc = c(toto[1:d,]$t_inc),
                                 t_inc_cent = c(toto[1:d,]$t_inc_cent)
                               ))
      }
      else{
        epidemic_data <- rbind(epidemic_data,
                               cbind(
                                 season = rep(i, d),
                                 weeks = 1:d,
                                 t_inc = c(toto$t_inc,
                                           rep(NA, d - l.toto)),
                                 t_inc_cent = c(toto$t_inc_cent,
                                                rep(NA, d - l.toto))
                               ))
        
      }
    }
  }
  epidemic_data <- epidemic_data[-(1:d),]
  return(epidemic_data)
}
```

```{r EpidemicDataFrame_cum}
#' @param data data frame with (at least) three columns (year, epid, t_inc) of type EpidemicDataFrame
#' @param d length of the Serfling epidemic 
#' @return a data frame with a year column, epidemic weeks and a incidence column with ILI rates of week 1, week 2 and size the epidemic 

EpidemicDataFrame_cum <- function(data) {
  season <- unique(data$season)
  epidemic_data <- data.frame(
    season = rep(season,each = 3),
    weeks = rep(1:3, length(season)),
    t_inc = rep(NA, 3*length(season)),
    t_inc_cent =rep(NA, 3*length(season)))
  
  for (i in unique(data$season)){
    temp <- subset(data, season == i)
    epidemic_data[(epidemic_data$season == i), ]$t_inc <- c(
      temp[temp$week == 1, ]$t_inc, 
      temp[temp$week == 2, ]$t_inc,
      sum(temp$t_inc, na.rm = T)
    )
    epidemic_data[(epidemic_data$season == i), ]$t_inc_cent <- c(
      temp[temp$week == 1, ]$t_inc_cent, 
      temp[temp$week == 2, ]$t_inc_cent,
      sum(temp$t_inc_cent, na.rm = T)
    )
  }
    return(epidemic_data)
}
```

## Density of a multivariate GPD with independent Gumbel generators

```{r fGumbelU_1}
#' @param t positive real
#' @param x a vector of dimension d
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return Integrand in the numerator in the density of a multivariate GPD with independent Gumbel generators
fGumbelU_1 <- function(t, x, alpha, beta) {
  d <- length(beta)
  y <- alpha * (x - beta)
  tointegrate <- 1
  for (j in 1:d) {
    tointegrate <-
      tointegrate * alpha[j] * t ^ (-alpha[j]) * exp(-y[j]) * exp(-(t ^ (-alpha[j]) *
                                                                      exp(-y[j])))
  }
  return(tointegrate)
}
```

```{r fGumbelU_2}
#' @param t positive real
#' @param x a vector of dimension d
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return Integrand in the denominator in the density of a multivariate GPD with independent Gumbel generators
fGumbelU_2 <- function(t, x, alpha, beta) {
  d <- length(beta)
  tointegrate <- 1
  for (j in 1:d) {
    tointegrate <-
      tointegrate * exp(-(t ^ (-alpha[j]) * exp(alpha[j] * beta[j])))
  }
  return(1 - tointegrate)
}
```

```{r DensityGumbelMGPDstand_U}
#' @param x a vector of dimension d
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return density of a multivariate GPD with independent Gumbel generators

DensityGumbelMGPDstand_U <- function(x, alpha, beta) {
  d <- length(alpha)
  if (length(unique(alpha)) == 1) {
    a <- unique(alpha)
    num <- a ^ (d - 1) * gamma(d - 1 / a) * prod(exp(-(a * (x - beta))))
    den <-
      (sum(exp(-(a * (
        x - beta
      ))))) ^ (d - 1 / a) * gamma(1 - 1 / a) * (sum(exp(beta * a))) ^ (1 / a)
    h <- num / den
  }
  else{
    res1 <-
      quadinf(
        fGumbelU_1,
        xa = 1e-3,
        xb = Inf,
        tol = 1e-15,
        x = x,
        alpha = alpha,
        beta = beta
      )
    res2 <-
      quadinf(
        f = fGumbelU_2,
        xa = 0,
        xb = Inf,
        x = x,
        alpha = alpha,
        beta = beta,
        tol = 1e-15
      )
    h <- res1$Q / res2$Q
    return(h)
  }
}
```

## Likelihood for a multivariate GPD model with independent Gumbel generators

```{r LLKGumbelMGPDstand_U}
#' @param p=c(a,b)  parameter
#' @param x a data.frame with years and with d incidences for each year of type EpidemicDataFrame
#' @param beta1 first component of beta to be fixed for identifiability
#' @return negative log-likelihood 

LLKGumbelMGPDstand_U <- function(p, x, beta1, lw, up){
  d<-dim(x)[2]
  alpha <- p[1:d]+1e-12
  beta <- c(beta1,p[-(1:d)])
 if(any(alpha<= lw[1])||any(alpha >=up[1])||any( beta<=lw[2]) ||any(beta >=up[2])){nll <- 1e12}
else{
  L<-apply(x,1,DensityGumbelMGPDstand_U,alpha=alpha,beta=beta)
  nll<--sum(log(L))}
  return(nll)
}
```

## Density of a multivariate GPD with independent reverse Gumbel generators

```{r fRevGumbelU_1}
#' @param t positive real
#' @param x a vector of dimension d
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return Integrand in the numerator in the density of a multivariate GPD with independent reverser Gumbel generators

fRevGumbelU_1 <- function(t, x, alpha, beta) {
  d <- length(beta)
  y <- alpha * (x - beta)
  tointegrate <- 1
  for (j in 1:d) {
    tointegrate <-
      tointegrate * alpha[j] * t ^ (alpha[j]) * exp(y[j]) * exp(-(t ^ (alpha[j]) *
                                                                    exp(y[j])))
  }
  return(tointegrate)
}
```


```{r fRevGumbelU_2}
#' @param t positive real
#' @param x a vector of dimension d
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return Integrand in the denominator in the density of a multivariate GPD with independent reverse Gumbel generators
fRevGumbelU_2 <- function(t, x, alpha, beta) {
  d <- length(beta)
  tointegrate <- 1
  for (j in 1:d) {
    tointegrate <-
      tointegrate * exp(-(t ^ (alpha[j]) * exp(-alpha[j] * beta[j])))
  }
  return(1 - tointegrate)
}
```


```{r DensityRevGumbelMGPDstand_U}
#' @param x a vector of dimension d
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return density of a multivariate GPD with independent reverse Gumbel generators

DensityRevGumbelMGPDstand_U <- function(x, alpha, beta) {

  res1 <-
    quadinf(
      fRevGumbelU_1,
      xa = 0.1,
      xb = Inf,
      tol = 1e-15,
      x = x,
      alpha = alpha,
      beta = beta
    )

  res2 <-
    quadinf(
      f = fRevGumbelU_2,
      xa = 0,
      xb = Inf,
      x = x,
      alpha = alpha,
      beta = beta,
      tol = 1e-15
    )

  h <- res1$Q / res2$Q
  return(h)
}
```

## Likelihood for a multivariate GPD model with independent reverse Gumbel generators

```{r LLKRevGumbelMGPDstand_U}
#' @param p=c(a,b)  parameter
#' @param x a data.frame with years and with d incidences for each year of type EpidemicDataFrame
#' @param beta1 first component of beta to be fixed for identifiability
#' @return negative log-likelihood 

LLKRevGumbelMGPDstand_U <- function(p, x, beta1, lw, up) {
  d <- dim(x)[2]
  alpha <- p[1:d] + 1e-12
  beta <- c(beta1, p[-(1:d)])
  if (any(alpha <= lw[1]) ||
      any(alpha >= up[1]) ||
      any(beta <= lw[2]) || any(beta >= up[2])) {
    nll <- 1e12
  }
  else{
    L <- apply(x,
               1,
               DensityRevGumbelMGPDstand_U,
               alpha = alpha,
               beta = beta)
    nll <- -sum(log(L))
  }
  return(nll)
}
```

## Density of a multivariate GPD with independent reverse exponential generators

```{r max_expU_Rexp_int}
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return Expectation of the exponential of the maximum of the d-dim vector U with independent reverse exponential generators

toint <- function(t, alpha,beta){
  d <- length(beta)
  tointegrate <- 1
  for (j in 1:d){
    temp <- min(1,exp(beta[j])*t)
    tointegrate <- tointegrate*(temp)^(alpha[j])
  }
  return(1-tointegrate)
}

max_expU_Rexp_int <- function(alpha,beta){
  res <- quadinf(toint, xa = 0, xb = Inf, tol = 1e-15,
                 alpha = alpha, beta = beta)
  return(res$Q)
}
```


```{r DensityRevExpoMGPDstand_U}
#' @param x a vector of dimension d
#' @param alpha a vector of dimension d
#' @param beta a vector of dimension d
#' @return density of a multivariate GPD with independent reverse Exponential generators

DensityRevExpoMGPDstand_U <-function(x,alpha, beta)
{
  EM <- max_expU_Rexp_int(alpha = alpha, beta = beta)
  num <- prod(alpha*exp(alpha*(x+beta)))
  den <- EM*((1+sum(alpha))*max(exp(x+beta))^(sum(alpha)+1))
  return(num/den)
}
```

## Likelihood for a multivariate GPD model with independent reverse Exponential generators

```{r LLKRevExpoMGPDstand_U}
#' @param p=c(a,b)  parameter
#' @param x a data.frame with years and with d incidences for each year of type EpidemicDataFrame
#' @param beta1 first component of beta to be fixed for identifiability
#' @return negative log-likelihood 

LLKRevExpoMGPDstand_U <- function(p, x, beta1, lw, up){
  d<-dim(x)[2]
  alpha <- p[1:d]+1e-12
  beta <- c(beta1,p[-(1:d)])
  if(any(alpha<= lw[1])||any(alpha >=up[1])||any( beta<=lw[2]) ||any(beta >=up[2])){nll <- 1e12}
  else{
  L<-apply(x,1,DensityRevExpoMGPDstand_U,alpha=alpha,beta=beta)
  nll<--sum(log(L))
  }
  return(nll)
}
```

## Likelihood for a multivariate Gumbel GPD model with beta fixed 

```{r LLKGumbelMGPDstand_U_alpha}
#' @param p  parameter = alpha
#' @param x a data.frame with years and with d incidences for each year of type EpidemicDataFrame
#' @param beta beta fixed 
#' @return negative log-likelihood for a multivariate Gumbel GPD model with beta fixed 

LLKGumbelMGPDstand_U_alpha <- function(p, x, beta, lw, up){
  d<-dim(x)[2]
  alpha <- p+1e-12
  if(any(alpha<= lw[1])||any(alpha >=up[1])){nll <- 1e12}
  else{
    L<-apply(x,1,DensityGumbelMGPDstand_U,alpha=alpha,beta=beta)
    nll<--sum(log(L))}
  return(nll)
}
```

## Likelihood for a multivariate Gumbel GPD model with all $\alpha$-s equal 

```{r LLKGumbelMGPDstand_U_abeta}
#' @param p  parameter = c(a, beta) with alpha = (a,a,...,d)
#' @param x a data.frame with years and with d incidences for each year of type EpidemicDataFrame
#' @param beta beta fixed 
#' @return negative log-likelihood for a multivariate Gumbel GPD model with all alpha equal 

LLKGumbelMGPDstand_U_abeta <- function(p, x, beta1, lw, up) {
  d <- dim(x)[2]
  alpha <- rep(p[1] + 1e-12, d)
  beta <- c(beta1, p[-1])
  if (any(alpha <= lw[1]) ||
      any(alpha >= up[1]) ||
      any(beta <= lw[2]) || any(beta >= up[2])) {
    nll <- 1e12
  }
  else{
    L <- apply(x,
               1,
               DensityGumbelMGPDstand_U,
               alpha = alpha,
               beta = beta)
    nll <- -sum(log(L))
  }
  return(nll)
}
```


## Likelihood for a multivariate Gumbel GPD model with $\beta$ fixed equal to 0 and all $\alpha$ equal

```{r LLKGumbelMGPDstand_U_a}
#' @param p  parameter = c(a, beta) with alpha = (a,a,...,d)
#' @param x a data.frame with years and with d incidences for each year of type EpidemicDataFrame
#' @param beta beta fixed 
#' @return negative log-likelihood for a multivariate Gumbel GPD model with beta fixed equal to 0 and all alpha equal

LLKGumbelMGPDstand_U_a <- function(p, x, beta, lw, up){
  d<-dim(x)[2]
  alpha <- rep(p[1]+1e-12,d)
  if(any(alpha<= lw[1])||any(alpha >=up[1])){nll <- 1e12}
  else{
    L<-apply(x,1,DensityGumbelMGPDstand_U,alpha=alpha,beta=beta)
    nll<--sum(log(L))}
  return(nll)
}
```

## Probability to be extreme given x1 and x2

```{r proba_extreme_3g12}
#' @param x12 Excesses of the two first weeks of a new epidemic 
#' @returm Probability to be extreme given the two first weeks of a new epidemic
proba_extreme_3g12 <- function(x12) {
  proba_extreme <- read.csv("ProbaExtremeWeek3.csv",
           row.names = 1)
  if (any(x12 > 0)) {
    res <- 1
  }
  else{
    res <- proba_extreme
  }
  return(res)
}
```

## Probability to be extreme given x1 and x2 for the size

```{r proba_extreme_3g12_cum}
#' @param x12 Excesses of the two first weeks of a new epidemic 
#' @returm Probability to be extreme given the two first weeks of a new epidemic
proba_extreme_3g12_cum <- function(x12) {
  proba_extreme <- read.csv("ProbaExtremeSize.csv",
           row.names = 1)
  if (any(x12 > 0)) {
    res <- 1
  }
  else{
    res <- proba_extreme
  }
  return(res)
}
```

## Density of a 1-d Gumbel r.v.

```{r marg.GumbelU}
#' @param x real 
#' @param alpha scale parameter
#' @param beta location parameter
#' @return the density of a one-dim Gumbel r.v. 

marg.GumbelU <- function(x, alpha, beta){
  f <- alpha*exp(-alpha*(x-beta))*exp(-exp(-alpha*(x-beta)))
  return(f)
}
```

## Conditionnal density of X3 given (X1,X2)

```{r condDensity}
#' @param t positive real 
#' @param a left endpoint of the interval of integration
#' @param x12 2-d vector representing the first components of x=(x1,x2,x3)
#' @param alpha scale parameter
#' @param beta location parameter
#' @return the conditionnal density of X3 given (X1,X2) 

condDensity <- function(t, a, x12, alpha, beta){
  x1 <- x12[1]
  x2 <- x12[2]
  f <- marg.GumbelU(x = x1+log(t), alpha = alpha[1], beta = beta[1])*marg.GumbelU(x = x2+log(t), alpha = alpha[2], beta = beta[2])*pevd(a+log(t), loc =beta[3], scale = 1/alpha[3], type = "Gumbel", lower.tail = FALSE)
  if (is.na(f)){f <- 0}
  return(f)
}
```

## Intregration of the conditionnal density 
```{r PredictInt}
#' @param a left endpoint of the interval of integration
#' @param x12 2-d vector representing the first components of x=(x1,x2,x3)
#' @param alpha scale parameter
#' @param beta location parameter
#' @return Integral of the conditionnal density of X3 given (X1,X2) on the interval [a, infty)

PredictInt <- function(a,x12,alpha,beta){
  res_pred <- quadinf(condDensity, xa = 0, xb =Inf, tol = 1e-10, a=a,  x12 = x12, alpha = alpha, 
                      beta=beta)
  return(res_pred$Q)
}
```

## Probability to exceed that the 3rd component exceeds a certain threshold given the first two components

```{r excessprobGumbelU_3g12}
#' @param v3 exceedance threshold 
#' @param x12 2-d vector representing the first components of x=(x1,x2,x3)
#' @param alpha scale parameter
#' @param beta location parameter
#' @return Probability to exceed that the 3rd component exceeds a certain threshold given the first two components 

excessprobGumbelU_3g12 <- function(v3, x12, alpha = alpha, beta=beta){
  if (any(x12>0)){
    num <- PredictInt(a = v3, x12 = x12, alpha = alpha, beta = beta)
    den <- PredictInt(a = -Inf, x12 = x12, alpha = alpha, beta = beta)
    res <- num/den
  }
  else if (v3 <=0) {res <- 1}
  else{      
    num <- PredictInt(a = v3, x12 = x12, alpha = alpha, beta = beta)
    den <- PredictInt(a = 0, x12 = x12, alpha = alpha, beta = beta)
    res <- num/den
  }
return(res)
}
```


## Leave-one-out 

```{r LOO_fit}
#' @param i loop index 
#' @param train_list training data set
#' @param thres_gpd GPD threshold
#' @return a matrix with the index i, estimates of the parameters


LOO_fit <- function(i, train_list, thres_gpd) {
  epid_data_LOO <- train_list[[i]]
  excess_matrix_LOO <-
    matrix(epid_data_LOO$excess_stand,
           ncol = d,
           byrow = T)

  #Standard joint estimation
  alpha0 <- est.alpha_M1
  b0 <- est.beta_M1[2:3]
  beta1 <- 0
  fitGumbelU_standard <-
    optim(
      par = c(alpha0, b0),
      fn = LLKGumbelMGPDstand_U,
      x = excess_matrix_LOO,
      beta1 = beta1,
      lw = c(1.1,-1.5),
      up = c(10, 1.5),
      control = list(maxit = 1e4, reltol = 10e-10)
    )
  est.alpha <- fitGumbelU_standard$par[1:d]
  est.beta <- c(beta1, fitGumbelU_standard$par[-(1:d)])
  return(matrix(c(i, est.alpha, est.beta), ncol = 7))
}
```


## Leave-one-out prediction 

```{r pred_parallel}
#' @param i loop index 
#' @param train_list training data set
#' @param thres_gpd GPD threshold
#' @return a matrix with the value of the excess of Week 3, GP prediction, Logistic prediction, value of the likelihood 

pred_parallel <- function(i, train_list, test_list) {
  epid_data_train <-
    data.frame(
      week1 = train_list[[i]][train_list[[i]]$weeks == 1, ]$excess_stand,
      week2 = train_list[[i]][train_list[[i]]$weeks ==
                                2, ]$excess_stand,
      week3 = train_list[[i]][train_list[[i]]$weeks ==
                                3, ]$excess_stand
    )
  epid_data_test <-
    data.frame(
      week1 = test_list[[i]][test_list[[i]]$weeks == 1, ]$excess_stand,
      week2 = test_list[[i]][test_list[[i]]$weeks ==
                                2, ]$excess_stand,
      week3 = test_list[[i]][test_list[[i]]$weeks ==
                                3, ]$excess_stand
    )
  est.alpha <- est.alpha_list[[i]]
  est.beta <- est.beta_list[[i]]
  ### Prediction
  excess3 <- epid_data_test$week3
  excess12 <- c(epid_data_test$week1, epid_data_test$week2)

  predMGPD <- rep(0, length(thres_pred))
  predLOGIT <- rep(0, length(thres_pred))

  for (j in 1:length(thres_pred)) {
    predMGPD[j] <-
      excessprobGumbelU_3g12(
        v3 = thres_pred[j],
        x12 = excess12 ,
        alpha = est.alpha,
        beta = est.beta
      )

    epid_data_train$outcome <- epid_data_train$week3 > thres_pred[j]
    fit <-
      brglm(
        formula = outcome ~ week1 + week2,
        data = epid_data_train,
        family = binomial,
        maxit = 100
      )

    predLOGIT[j] <-
      exp(
        fit$coefficients[1] + fit$coefficients[2] * epid_data_test$week1 + fit$coefficients[3] *
          epid_data_test$week2
      ) / (
        1 + exp(
          fit$coefficients[1] + fit$coefficients[2] * epid_data_test$week1 + fit$coefficients[3] *
            epid_data_test$week2
        )
      )
  }
  excess_matrix_test <- c(epid_data_test$week1, epid_data_test$week2,epid_data_test$week3)
  LLK <-
    DensityGumbelMGPDstand_U(x = excess_matrix_test,
                             alpha = est.alpha,
                             beta = est.beta)
  return(matrix(c(excess3, predMGPD, predLOGIT, LLK), ncol = 12))
}
```


## Functions for parallel fit for simulations

```{r FitParallelSimus}
#' @param i loop index 
#' @param excess_list list of train sets
#' @return a matrix with the index i, estimated parameters, maximised negative likelihood   
 FitParallelSimus <- function(i, excess_list){
  excess_matrix <- excess_list[[i]]
  excess_matrix_train <- excess_matrix[1:n_train, ]
  alpha0 <- alpha[1:d]
  b0 <- beta[2:d]
  beta1 <- 0
  fitGumbelU_standard <- optim(par = c(alpha0,b0),fn=LLKGumbelMGPDstand_U,
                               x = excess_matrix_train,
                               beta1 =beta1,
                               lw = c(1.1, -1.5),
                               up = c(7, 1.5), control = list(maxit = 1e4, reltol = 10e-10))
  est.alpha <- fitGumbelU_standard$par[1:d]
  est.beta <- c(beta1, fitGumbelU_standard$par[-(1:d)])
  LLK <- fitGumbelU_standard$value

  return(matrix(c(i,est.alpha, est.beta, LLK), ncol = 8))
}
```

## Function for parallel prediction for simulated data Week 3

```{r PredParallelSimus}
#' @param i loop index 
#' @param split_index the index of the different datasets
#' @return a matrix with the value of the excess of Week 3, GP prediction, logistic prediction, the negative likelihood  
PredParallelSimus <- function(i, split_index) {
  excess_matrix <- excess_list[[i]]
  excess_matrix_train <- excess_matrix[1:n_train, ]
  epid_data_train <- data.frame(
    season = 1:n_train,
    week1 = excess_matrix_train[, 1],
    week2 = excess_matrix_train[, 2],
    week3 = excess_matrix_train[, 3]
  )
  excess_matrix_test <- excess_matrix[n_train + n_test,]

  est.alpha <- est.alpha_list[[i]]
  est.beta <- est.beta_list[[i]]
  ### Prediction
  epid_data_test <- data.frame(
    indice = i,
    week1 = excess_matrix_test[1],
    week2 = excess_matrix_test[2],
    week3 = excess_matrix_test[3]
  )
  excess3 <- excess_matrix_test[3]
  excess12 <- excess_matrix_test[1:2]

  predMGPD <- rep(0, length(thres_pred))
  predLOGIT <- rep(0, length(thres_pred))

  for (j in 1:length(thres_pred)) {
    predMGPD[j] <-
      excessprobGumbelU_3g12(
        v3 = thres_pred[j],
        x12 = excess12 ,
        alpha = est.alpha,
        beta = est.beta
      )

    epid_data_train$outcome <- epid_data_train$week3 > thres_pred[j]
    fit <-
      brglm(
        formula = outcome ~ week1 + week2,
        data = epid_data_train,
        family = binomial,
        maxit = 100
      )

    predLOGIT[j] <-
      exp(
        fit$coefficients[1] + fit$coefficients[2] * epid_data_test$week1 + fit$coefficients[3] *
          epid_data_test$week2
      ) / (
        1 + exp(
          fit$coefficients[1] + fit$coefficients[2] * epid_data_test$week1 + fit$coefficients[3] *
            epid_data_test$week2
        )
      )
  }

  LLK <-
    DensityGumbelMGPDstand_U(x = excess_matrix_test,
                             alpha = est.alpha,
                             beta = est.beta)
  return(matrix(c(excess3, predMGPD, predLOGIT, LLK), ncol = 12))
}
```

## Parallel prediction with True model 

```{r PredParallelTrue}
#' @param i loop index 
#' @param split_index the index of the different datasets
#' @return a matrix with the value of the excess of Week 3, GP prediction with True Gumbel model
PredParallelTrue <- function(i, split_index){
  excess_matrix <- excess_list[[i]] 
  excess_matrix_train <- excess_matrix[1:n_train,]
    epid_data_train <- data.frame(
      season = 1:n_train,
      week1 =
        excess_matrix_train[, 1],
      week2 = excess_matrix_train[, 2],
      week3 =
        excess_matrix_train[, 3]) 
    excess_matrix_test <- excess_matrix[n_train + n_test, ]
    
    ### Prediction
    excess3 <- excess_matrix_test[3]
    excess12 <- excess_matrix_test[1:2]
    
    predMGPD <- rep(0, length(thres_pred))
    
    for (j in 1:length(thres_pred)) {
      predMGPD[j] <- excessprobGumbelU_3g12(
        v3 = thres_pred[j],
        x12 = excess12 ,
        alpha = alpha,
        beta = beta
      )
    }
    return(matrix(c(excess3, predMGPD), ncol = 6))
}
```
