---
title: "Codes for Simulated data for Week 3"
output:
  html_document:
    df_print: paged
    fig_caption : yes
---

## Preamble
```{r options}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,  fig.path = "figures/", fig.process = function(filename) {
    new_filename <- stringr::str_remove(string = filename,
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
  })
```

```{r setting packages}
libs <- c("ggplot2", "pracma", "glmnet", "extRemes", "foreach", "doParallel", "gridExtra", "pROC", "MLmetrics")
sapply(libs,require,character.only = T, quietly = TRUE, warn.conflicts = FALSE)
set.seed(29106799)
```

```{r function files}
require(knitr,quietly=TRUE,warn.conflicts = FALSE)
knit("PredictEpidemicTools.Rmd",quiet = TRUE)
```

```{r parallel coding settings}
detectCores()
cl <- makeCluster(35) #set to number of cores -1

registerDoParallel(cl)

getDoParWorkers()
```

## Import the simulated data

```{r import simulated data}
simul.dataU_Gumbel <- read.csv("SimulatedDataWeek3.csv", row.names = 1)

nb.epid_simus <- dim(simul.dataU_Gumbel)[1] / (33*3)
d <- dim(simul.dataU_Gumbel)[2]
```

## Parameters of the fitted Gumbel model 

```{r parameters}
est.param <-
  read.csv(
    "EstimatesParametersWeek3.csv",
    row.names = 1
  )
alpha <- as.matrix(est.param)[1, ]
beta <- as.matrix(est.param)[2, ]
```

## Preparation of the data

```{r data}
season_data <- unique(simul.dataU_Gumbel$season)
simul_excess_stand_matrix <-
  matrix(simul.dataU_Gumbel$excess, ncol = d, byrow = T)
n <- dim(simul_excess_stand_matrix)[1]

nb_replicates <- n / 33 ##nb of datasets of 33 epidemics
split_index <- split(1:n, 1:nb_replicates)
```

Number of datasets of 33 epidemics = `r nb_replicates`. 

## Define train sets

```{r train sets}
n_train <- 32
n_test <- 1

excess_list <- list()
for (i in 1:nb_replicates) {
  excess_list[[i]] <- simul_excess_stand_matrix[split_index[[i]],]
}
```

## Parallel fit of a Gumbel model for each train set

```{r parallel fit }
Res.fit_parallel <- foreach(
  i = 1:nb_replicates,
  .packages = c("pracma", "extRemes"),
  .combine = rbind) %dopar% {
  FitParallelSimus_Week3(i,excess_list = excess_list)
}

res.fitSimus_week3 <- data.frame(Res.fit_parallel)
colnames(res.fitSimus_week3) <- c("Indice", "alpha1", "alpha2","alpha3", "beta1", "beta2", "beta3","LLK")

```

## Lists of estimated parameters

```{r estimated parameters}
est.alpha_list <- list()
for (i in 1:nb_replicates) {
  est.alpha_list [[i]] <-
    c(
      res.fitSimus_week3[i,]$alpha1,
      res.fitSimus_week3[i,]$alpha2,
      res.fitSimus_week3[i,]$alpha3
    )
}

est.beta_list <- list()
for (i in 1:nb_replicates) {
  est.beta_list [[i]] <-
    c(
      res.fitSimus_week3[i,]$beta1,
      res.fitSimus_week3[i,]$beta2,
      res.fitSimus_week3[i,]$beta3
    )
}
```


## Get fixed prediction thresholds
```{r pred thresholds}
thres_pred <-
  read.csv(
    "FixedPredThresWeek3.csv",
    row.names = 1
  )
thres_pred <- as.vector(t(thres_pred))
```


## Parallel prediction for each simulated data set

```{r parallel pred Week 3 GPD}
res_parallel <- foreach(
  i = 1:nb_replicates,
  .packages = c("pracma", "extRemes"),
  .combine = rbind
) %dopar% {
  PredParallelSimusGPD(i, excess_list = excess_list, thres_pred = thres_pred)
}


res_week3_GPD <- data.frame(res_parallel)
colnames(res_week3_GPD) <-
  c(
    "Week3",
    "Predict_Gumbel_05",
    "Predict_Gumbel_075",
    "Predict_Gumbel_095",
    "Predict_Gumbel_1",
    "Predict_Gumbel_12",
    "LLK"
  )
```

```{r parallel pred Week 3 Logit}
res_parallel <- foreach(
  i = 1:nb_replicates,
  .packages = c("glmnet"),
  .combine = rbind
) %dopar% {
  PredParallelSimusLogit(i, excess_list = excess_list, thres_pred = thres_pred)
}


res_week3_Logit <- data.frame(res_parallel)
colnames(res_week3_Logit) <-
  c(
    "Predict_Logit_05",
    "Predict_Logit_075",
    "Predict_Logit_095",
    "Predict_Logit_1",
    "Predict_Logit_12"
  )
```

```{r}
res_week3 <- cbind(res_week3_GPD, res_week3_Logit)
write.csv(x = res_week3, file = "PredSimus_Week3.csv")
```


## Prediction with true model

```{r pred parallel true}
res_parallel_true <- foreach(
  i = 1:nb_replicates,
  .combine = rbind
) %dopar% {
  PredParallelTrue(i, excess_list = excess_list, thres_pred = thres_pred)
}


res_true_week3 <- data.frame(res_parallel_true)
colnames(res_true_week3) <-
  c(
    "Week3",
    "Predict_True_05",
    "Predict_True_075",
    "Predict_True_095",
    "Predict_True_1",
    "Predict_True_12"
  )

res_week3 <- cbind(res_week3, res_true_week3[, -1])
```

```{r}
write.csv(x = res_week3, file = "PredSimus_Week3.csv")
```

## Boxplots (Figures 5 and 6 a) b) c) and d))
```{r}
thres_pred <-
  read.csv(
    "FixedPredThresWeek3.csv",
    row.names = 1
  )
thres_pred <- as.vector(t(thres_pred))

res_week3 <- read.csv(file = "PredSimus_Week3.csv", row.names = 1)
```

### Threshold 864 ($\kappa = 0.5$)


```{r res_week3_05}
res_week3_05 <-
  subset(res_week3,
         select = c(Week3, Predict_Gumbel_05, Predict_Logit_05, Predict_True_05))
res_week3_05$Outcome <-
  as.numeric(res_week3_05$Week3 > thres_pred[1])
```

```{r BrierSimus05_GP}
BrierSimus05_GP <-
  ggplot(data = res_week3_05, aes(x = as.factor(Outcome), y = Predict_Gumbel_05))
BrierSimus05_GP <-
  BrierSimus05_GP + geom_boxplot(outlier.size = 0.5,
                        outlier.shape = 1,
                        size = 0.5)
BrierSimus05_GP <- BrierSimus05_GP + ggtitle(TeX('Level = 816 ($\\kappa =0.5$)'))
BrierSimus05_GP <-
  BrierSimus05_GP + xlab("Outcome") + ylab("Prediction probability")
BrierSimus05_GP <- BrierSimus05_GP + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus05_GP <- BrierSimus05_GP + ylim(0,1)
BrierSimus05_GP
```

```{r BrierSimus05_Logistic}
BrierSimus05_Logistic <-
  ggplot(data = res_week3_05, aes(x = as.factor(Outcome), y = Predict_Logit_05))
BrierSimus05_Logistic <-
  BrierSimus05_Logistic +  geom_boxplot(outlier.size = 0.5,
                         outlier.shape = 1,
                         size = 0.5)
BrierSimus05_Logistic <- BrierSimus05_Logistic + ggtitle(TeX('Level = 864 ($\\kappa =0.5$)'))
BrierSimus05_Logistic <-
  BrierSimus05_Logistic + xlab("Outcome") + ylab("Prediction probability")
BrierSimus05_Logistic <- BrierSimus05_Logistic + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus05_Logistic <- BrierSimus05_Logistic + ylim(0,1)
```

```{r BrierSimus05_True}
BrierSimus05_True <-
  ggplot(data = res_week3_05, aes(x = as.factor(Outcome), y = Predict_True_05))
BrierSimus05_True <-
  BrierSimus05_True +  geom_boxplot(outlier.size = 0.5,
                         outlier.shape = 1,
                         size = 0.5)
BrierSimus05_True <- BrierSimus05_True + ggtitle(TeX('Level = 864 ($\\kappa =0.5$)'))
BrierSimus05_True <-
  BrierSimus05_True + xlab("Outcome") + ylab("Prediction probability")
BrierSimus05_True <- BrierSimus05_True + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus05_True <- BrierSimus05_True + ylim(0,1)
```

```{r pr.data05}
dis.thres05_LOGIT <- sort(res_week3_05$Predict_Logit_05, decreasing = TRUE) 
 pr.data05_LOGIT <-
  data.frame(DisThres = dis.thres05_LOGIT, Model = rep("Logistic", length(dis.thres05_LOGIT)))
  for (i in 1:length(dis.thres05_LOGIT)) {
  pr.data05_LOGIT$Precision[i] <- sum((res_week3_05$Outcome == 1) &
                                      (res_week3_05$Predict_Logit_05 > dis.thres05_LOGIT[i]) , na.rm = T 
                                    ) / sum((res_week3_05$Predict_Logit_05 > dis.thres05_LOGIT[i]), na.rm = T)
  pr.data05_LOGIT$Recall[i] <- sum((res_week3_05$Outcome == 1) &
                                      (res_week3_05$Predict_Logit_05 > dis.thres05_LOGIT[i]), na.rm = T 
                                    ) / sum( (res_week3_05$Outcome == 1))
}


dis.thres05_MGPD <- sort(res_week3_05$Predict_Gumbel_05, decreasing = TRUE)
pr.data05_MGPD <-
  data.frame(DisThres = c(dis.thres05_MGPD),
             Model = rep("Gumbel", length(dis.thres05_MGPD)))

for (i in 1:length(dis.thres05_MGPD)) {
   pr.data05_MGPD$Precision[i] <- sum((res_week3_05$Outcome == 1) &
                                      (res_week3_05$Predict_Gumbel_05 > dis.thres05_MGPD[i]) , na.rm = T 
                                    ) / sum((res_week3_05$Predict_Gumbel_05 > dis.thres05_MGPD[i]) )
  pr.data05_MGPD$Recall[i] <- sum((res_week3_05$Outcome == 1) &
                                      (res_week3_05$Predict_Gumbel_05 > dis.thres05_MGPD[i]), na.rm = T 
                                    ) / sum( (res_week3_05$Outcome == 1))
}

dis.thres05_TRUE <- sort(res_week3_05$Predict_True_05, decreasing = TRUE)

pr.data05_TRUE <-
  data.frame(DisThres = c(dis.thres05_TRUE),
             Model = rep("True", length(dis.thres05_TRUE)))
for (i in 1:length(dis.thres05_TRUE)) {

     pr.data05_TRUE$Precision[i] <- sum((res_week3_05$Outcome == 1) &
                                      (res_week3_05$Predict_True_05 > dis.thres05_TRUE[i]) , na.rm = T 
                                    ) / sum((res_week3_05$Predict_True_05 > dis.thres05_TRUE[i]) )
  pr.data05_TRUE$Recall[i] <- sum((res_week3_05$Outcome == 1) &
                                      (res_week3_05$Predict_True_05 > dis.thres05_TRUE[i]), na.rm = T 
                                    ) / sum( (res_week3_05$Outcome == 1))
}

pr.data05 <- rbind(pr.data05_MGPD, pr.data05_LOGIT) #rbind(pr.data05_MGPD, pr.data05_LOGIT, pr.data05_TRUE)
```

```{r  PRCSimus_05}
PRCSimus_05 <-
  ggplot(data = pr.data05, aes(
    x = Recall,
    y = Precision,
    colour = Model,
    linetype = Model
  )) + geom_path()
PRCSimus_05 <- PRCSimus_05 + geom_hline(yintercept = sum( (res_week3_05$Outcome == 1))/length(res_week3_05$Outcome))
PRCSimus_05 <- PRCSimus_05 + xlim(c(0, 1)) + ylim(c(0, 1))
PRCSimus_05 <- PRCSimus_05 + scale_color_manual(values = c("blue", "red"))
PRCSimus_05 <- PRCSimus_05 + xlab("Recall") + ylab("Precision")
PRCSimus_05 <- PRCSimus_05 + ggtitle(TeX('Level = 864 ($\\kappa =0.5$)'))
PRCSimus_05 <- PRCSimus_05 + theme(
  panel.grid.minor = element_blank(),
 text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18),
  legend.title=element_text(size=12), 
  legend.text=element_text(size=12)
)
```

### Threshold  1,297 ($\kappa = 0.75$)

```{r res_week3_075}
res_week3_075 <-
  subset(res_week3,
         select = c(
           Week3,
           Predict_Gumbel_075,
           Predict_Logit_075,
           Predict_True_075
         ))
res_week3_075$Outcome <-
  as.numeric(res_week3_075$Week3 > thres_pred[2])
```

```{r BrierSimus075_GP}
BrierSimus075_GP <-
  ggplot(data = res_week3_075, aes(x = as.factor(Outcome), y = Predict_Gumbel_075))
BrierSimus075_GP <-
  BrierSimus075_GP + geom_boxplot(outlier.size = 0.5,
                        outlier.shape = 1,
                        size = 0.5)
BrierSimus075_GP <- BrierSimus075_GP + ggtitle(TeX('Level = $1,297$ ($\\kappa =0.75$)'))
BrierSimus075_GP <-
  BrierSimus075_GP + xlab("Outcome") + ylab("Prediction probability")
BrierSimus075_GP <- BrierSimus075_GP + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus075_GP <- BrierSimus075_GP + ylim(0,1)
BrierSimus075_GP
```

```{r BrierSimus075_Logistic}
BrierSimus075_Logistic <-
  ggplot(data = res_week3_075, aes(x = as.factor(Outcome), y = Predict_Logit_075))
BrierSimus075_Logistic <-
  BrierSimus075_Logistic + geom_boxplot(outlier.size = 0.5,
                        outlier.shape = 1,
                        size = 0.5)
BrierSimus075_Logistic <- BrierSimus075_Logistic + ggtitle(TeX('Level = $1,297$ ($\\kappa =0.75$)'))
BrierSimus075_Logistic <-
  BrierSimus075_Logistic + xlab("Outcome") + ylab("Prediction probability")
BrierSimus075_Logistic <- BrierSimus075_Logistic + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus075_Logistic <- BrierSimus075_Logistic + ylim(0,1)
```

```{r BrierSimus075_True}
BrierSimus075_True <-
  ggplot(data = res_week3_075, aes(x = as.factor(Outcome), y = Predict_True_075))
BrierSimus075_True <-
  BrierSimus075_True +  geom_boxplot(outlier.size = 0.5,
                         outlier.shape = 1,
                         size = 0.5)
BrierSimus075_True <- BrierSimus075_True + ggtitle(TeX('Level = $1,297$ ($\\kappa =0.75$)'))
BrierSimus075_True <-
  BrierSimus075_True + xlab("Outcome") + ylab("Prediction probability")
BrierSimus075_True <- BrierSimus075_True + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus075_True <- BrierSimus075_True + ylim(0,1)
```

```{r pr.data075}
dis.thres075_LOGIT <- sort(res_week3_075$Predict_Logit_075, decreasing = TRUE) 
 pr.data075_LOGIT <-
  data.frame(DisThres = dis.thres075_LOGIT, Model = rep("Logistic", length(dis.thres075_LOGIT)))
  for (i in 1:length(dis.thres075_LOGIT)) {
  pr.data075_LOGIT$Precision[i] <- sum((res_week3_075$Outcome == 1) &
                                      (res_week3_075$Predict_Logit_075 > dis.thres075_LOGIT[i]) , na.rm = T 
                                    ) / sum((res_week3_075$Predict_Logit_075 > dis.thres075_LOGIT[i]), na.rm = T)
  pr.data075_LOGIT$Recall[i] <- sum((res_week3_075$Outcome == 1) &
                                      (res_week3_075$Predict_Logit_075 > dis.thres075_LOGIT[i]), na.rm = T 
                                    ) / sum( (res_week3_075$Outcome == 1))
}


dis.thres075_MGPD <- sort(res_week3_075$Predict_Gumbel_075, decreasing = TRUE)
pr.data075_MGPD <-
  data.frame(DisThres = c(dis.thres075_MGPD),
             Model = rep("Gumbel", length(dis.thres075_MGPD)))

for (i in 1:length(dis.thres075_MGPD)) {
   pr.data075_MGPD$Precision[i] <- sum((res_week3_075$Outcome == 1) &
                                      (res_week3_075$Predict_Gumbel_075 > dis.thres075_MGPD[i]) , na.rm = T 
                                    ) / sum((res_week3_075$Predict_Gumbel_075 > dis.thres075_MGPD[i]) )
  pr.data075_MGPD$Recall[i] <- sum((res_week3_075$Outcome == 1) &
                                      (res_week3_075$Predict_Gumbel_075 > dis.thres075_MGPD[i]), na.rm = T 
                                    ) / sum( (res_week3_075$Outcome == 1))
}

dis.thres075_TRUE <- sort(res_week3_075$Predict_True_075, decreasing = TRUE)
pr.data075_TRUE <-
  data.frame(DisThres = c(dis.thres075_TRUE),
             Model = rep("True", length(dis.thres075_TRUE)))
for (i in 1:length(dis.thres075_TRUE)) {

     pr.data075_TRUE$Precision[i] <- sum((res_week3_075$Outcome == 1) &
                                      (res_week3_075$Predict_True_075 > dis.thres075_TRUE[i]) , na.rm = T 
                                    ) / sum((res_week3_075$Predict_True_075 > dis.thres075_TRUE[i]) )
  pr.data075_TRUE$Recall[i] <- sum((res_week3_075$Outcome == 1) &
                                      (res_week3_075$Predict_True_075 > dis.thres075_TRUE[i]), na.rm = T 
                                    ) / sum( (res_week3_075$Outcome == 1))
}

pr.data075 <- rbind(pr.data075_MGPD, pr.data075_LOGIT)#, pr.data075_TRUE)
```

```{r  PRCSimus_075}
PRCSimus_075 <-
  ggplot(data = pr.data075, aes(
    x = Recall,
    y = Precision,
    colour = Model,
    linetype = Model
  )) + geom_path()
PRCSimus_075 <- PRCSimus_075 + geom_hline(yintercept = sum( (res_week3_075$Outcome == 1))/length(res_week3_075$Outcome))
PRCSimus_075 <- PRCSimus_075 + xlim(c(0, 1)) + ylim(c(0, 1))
PRCSimus_075 <- PRCSimus_075 + scale_color_manual(values = c("blue", "red"))
PRCSimus_075 <- PRCSimus_075 + xlab("Recall") + ylab("Precision")
PRCSimus_075 <- PRCSimus_075 + ggtitle(TeX('Level = $1,297$ ($\\kappa =0.75$)'))
PRCSimus_075 <- PRCSimus_075 + theme(
  panel.grid.minor = element_blank(),
 text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18),
  legend.title=element_text(size=12), 
  legend.text=element_text(size=12)
)
PRCSimus_075
```

### Threshold  1,642 ($\kappa = 0.95$)

```{r res_week3_095}
res_week3_095 <-
  subset(res_week3,
         select = c(
           Week3,
           Predict_Gumbel_095,
           Predict_True_095
         ))
res_week3_095$Outcome <-
  as.numeric(res_week3_095$Week3 > thres_pred[3])
```

```{r BrierSimus095_GP}
BrierSimus095_GP <-
  ggplot(data = res_week3_095, aes(x = as.factor(Outcome), y = Predict_Gumbel_095))
BrierSimus095_GP <-
  BrierSimus095_GP + geom_boxplot(outlier.size = 0.5,
                        outlier.shape = 1,
                        size = 0.5)
BrierSimus095_GP <- BrierSimus095_GP + ggtitle(TeX('Level = $1,643$ ($\\kappa =0.95$)'))
BrierSimus095_GP <-
  BrierSimus095_GP + xlab("Outcome") + ylab("Prediction probability")
BrierSimus095_GP <- BrierSimus095_GP + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus095_GP <- BrierSimus095_GP + ylim(0,1)
```


```{r BrierSimus095_True}
BrierSimus095_True <-
  ggplot(data = res_week3_095, aes(x = as.factor(Outcome), y = Predict_True_095))
BrierSimus095_True <-
  BrierSimus095_True +  geom_boxplot(outlier.size = 0.5,
                         outlier.shape = 1,
                         size = 0.5)
BrierSimus095_True <- BrierSimus095_True + ggtitle(TeX('Level = $1,643$ ($\\kappa =0.95$)'))
BrierSimus095_True <-
  BrierSimus095_True + xlab("Outcome") + ylab("Prediction probability")
BrierSimus095_True <- BrierSimus095_True + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus095_True <- BrierSimus095_True + ylim(0,1)
```

```{r pr.data095}
dis.thres095_MGPD <- sort(res_week3_095$Predict_Gumbel_095, decreasing = TRUE)
pr.data095_MGPD <-
  data.frame(DisThres = c(dis.thres095_MGPD),
             Model = rep("Gumbel", length(dis.thres095_MGPD)))

for (i in 1:length(dis.thres095_MGPD)) {
   pr.data095_MGPD$Precision[i] <- sum((res_week3_095$Outcome == 1) &
                                      (res_week3_095$Predict_Gumbel_095 > dis.thres095_MGPD[i]) , na.rm = T 
                                    ) / sum((res_week3_095$Predict_Gumbel_095 > dis.thres095_MGPD[i]) )
  pr.data095_MGPD$Recall[i] <- sum((res_week3_095$Outcome == 1) &
                                      (res_week3_095$Predict_Gumbel_095 > dis.thres095_MGPD[i]), na.rm = T 
                                    ) / sum( (res_week3_095$Outcome == 1))
}

dis.thres095_TRUE <- sort(res_week3_095$Predict_True_095, decreasing = TRUE)

pr.data095_TRUE <-
  data.frame(DisThres = c(dis.thres095_TRUE),
             Model = rep("True", length(dis.thres095_TRUE)))
for (i in 1:length(dis.thres095_TRUE)) {

     pr.data095_TRUE$Precision[i] <- sum((res_week3_095$Outcome == 1) &
                                      (res_week3_095$Predict_True_095 > dis.thres095_TRUE[i]) , na.rm = T 
                                    ) / sum((res_week3_095$Predict_True_095 > dis.thres095_TRUE[i]) )
  pr.data095_TRUE$Recall[i] <- sum((res_week3_095$Outcome == 1) &
                                      (res_week3_095$Predict_True_095 > dis.thres095_TRUE[i]), na.rm = T 
                                    ) / sum( (res_week3_095$Outcome == 1))
}

pr.data095 <- rbind(pr.data095_MGPD)#, pr.data095_TRUE)
```


```{r  PRCSimus_095}
PRCSimus_095 <-
  ggplot(data = pr.data095, aes(
    x = Recall,
    y = Precision,
    colour = Model,
    linetype = Model
  )) + geom_path()
PRCSimus_095 <- PRCSimus_095 + geom_hline(yintercept = sum( (res_week3_095$Outcome == 1))/length(res_week3_095$Outcome))
PRCSimus_095 <- PRCSimus_095 + xlim(c(0, 1)) + ylim(c(0, 1))
PRCSimus_095 <- PRCSimus_095 + scale_color_manual(values = c("blue"))
PRCSimus_095 <- PRCSimus_095 + xlab("Recall") + ylab("Precision")
PRCSimus_095 <- PRCSimus_095 + ggtitle(TeX('Level = $1,643$ ($\\kappa =0.95$)'))
PRCSimus_095 <- PRCSimus_095 + theme(
  panel.grid.minor = element_blank(),
 text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18),
  legend.title=element_text(size=12), 
  legend.text=element_text(size=12)
)
PRCSimus_095
```

### Threshold  1,729 ($\kappa = 1$)

```{r res_week3_1}
res_week3_1 <-
  subset(res_week3, select = c(Week3, Predict_Gumbel_1, Predict_True_1))
res_week3_1$Outcome <- as.numeric(res_week3_1$Week3 > thres_pred[4])
```

```{r BrierSimus1_GP}
BrierSimus1_GP <-
  ggplot(data = res_week3_1, aes(x = as.factor(Outcome), y = Predict_Gumbel_1))
BrierSimus1_GP <-
  BrierSimus1_GP + geom_boxplot(outlier.size = 0.5,
                        outlier.shape = 1,
                        size = 0.5)
BrierSimus1_GP <- BrierSimus1_GP + ggtitle(TeX('Level = $1,729$ ($\\kappa =1$)'))
BrierSimus1_GP <-
  BrierSimus1_GP + xlab("Outcome") + ylab("Prediction probability")
BrierSimus1_GP <- BrierSimus1_GP + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus1_GP <- BrierSimus1_GP + ylim(0,1)
```

```{r BrierSimus1_True}
BrierSimus1_True <-
  ggplot(data = res_week3_1, aes(x = as.factor(Outcome), y = Predict_True_1))
BrierSimus1_True <-
  BrierSimus1_True +  geom_boxplot(outlier.size = 0.5,
                         outlier.shape = 1,
                         size = 0.5)
BrierSimus1_True <- BrierSimus1_True + ggtitle(TeX('Level = $1,729$ ($\\kappa =1$)'))
BrierSimus1_True <-
  BrierSimus1_True + xlab("Outcome") + ylab("Prediction probability")
BrierSimus1_True <- BrierSimus1_True + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus1_True <- BrierSimus1_True + ylim(0,1)
```

```{r pr.data1}
dis.thres1_MGPD <- sort(res_week3_1$Predict_Gumbel_1, decreasing = TRUE)
pr.data1_MGPD <-
  data.frame(DisThres = c(dis.thres1_MGPD),
             Model = rep("Gumbel", length(dis.thres1_MGPD)))

for (i in 1:length(dis.thres1_MGPD)) {
   pr.data1_MGPD$Precision[i] <- sum((res_week3_1$Outcome == 1) &
                                      (res_week3_1$Predict_Gumbel_1 > dis.thres1_MGPD[i]) , na.rm = T 
                                    ) / sum((res_week3_1$Predict_Gumbel_1 > dis.thres1_MGPD[i]) )
  pr.data1_MGPD$Recall[i] <- sum((res_week3_1$Outcome == 1) &
                                    (res_week3_1$Predict_Gumbel_1 > dis.thres1_MGPD[i]), na.rm = T 
                                    ) / sum( (res_week3_1$Outcome == 1))
}

dis.thres1_TRUE <- sort(res_week3_1$Predict_True_1, decreasing = TRUE)

pr.data1_TRUE <-
  data.frame(DisThres = c(dis.thres1_TRUE),
             Model = rep("True", length(dis.thres1_TRUE)))
for (i in 1:length(dis.thres1_TRUE)) {

     pr.data1_TRUE$Precision[i] <- sum((res_week3_1$Outcome == 1) &
                                      (res_week3_1$Predict_True_1 > dis.thres1_TRUE[i]) , na.rm = T 
                                    ) / sum((res_week3_1$Predict_True_1 > dis.thres1_TRUE[i]) )
  pr.data1_TRUE$Recall[i] <- sum((res_week3_1$Outcome == 1) &
                                      (res_week3_1$Predict_True_1 > dis.thres1_TRUE[i]), na.rm = T 
                                    ) / sum( (res_week3_1$Outcome == 1))
}

pr.data1 <- rbind(pr.data1_MGPD)#, pr.data1_TRUE)
```

```{r  PRCSimus_1}
PRCSimus_1 <-
  ggplot(data = pr.data1, aes(
    x = Recall,
    y = Precision,
    colour = Model,
    linetype = Model
  )) + geom_path()
PRCSimus_1 <- PRCSimus_1 + geom_hline(yintercept = sum( (res_week3_1$Outcome == 1))/length(res_week3_1$Outcome))
PRCSimus_1 <- PRCSimus_1 + xlim(c(0, 1)) + ylim(c(0, 1))
PRCSimus_1 <- PRCSimus_1 + scale_color_manual(values = c("blue"))
PRCSimus_1 <- PRCSimus_1 + xlab("Recall") + ylab("Precision")
PRCSimus_1 <- PRCSimus_1 + ggtitle(TeX('Level = $1,729$ ($\\kappa =1$)'))
PRCSimus_1 <- PRCSimus_1 + theme(
  panel.grid.minor = element_blank(),
 text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18),
  legend.title=element_text(size=12), 
  legend.text=element_text(size=12)
)
PRCSimus_1
```

### Threshold 2,075 ($\kappa = 1.2$) --- not shown in the paper
```{r res_week3_12}
res_week3_12 <-
  subset(res_week3, select = c(Week3, Predict_Gumbel_12, Predict_True_12))
res_week3_12$Outcome <-
  as.numeric(res_week3_12$Week3 > thres_pred[5])
```

```{r BrierSimus12_GP}
BrierSimus12_GP <-
  ggplot(data = res_week3_12, aes(x = as.factor(Outcome), y = Predict_Gumbel_12))
BrierSimus12_GP <-
  BrierSimus12_GP + geom_boxplot(outlier.size = 0.5,
                        outlier.shape = 1,
                        size = 0.5)
BrierSimus12_GP <- BrierSimus12_GP + ggtitle(TeX('Level = $2,075$ ($\\kappa =1.2$)'))
BrierSimus12_GP <-
  BrierSimus12_GP + xlab("Outcome") + ylab("Prediction probability")
BrierSimus12_GP <- BrierSimus12_GP + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus12_GP <- BrierSimus12_GP + ylim(0,1)
BrierSimus12_GP
```

```{r BrierSimus12_True}

BrierSimus12_True <-
  ggplot(data = res_week3_12, aes(x = as.factor(Outcome), y = Predict_True_12))
BrierSimus12_True <-
  BrierSimus12_True +  geom_boxplot(outlier.shape = 1, size = 0.5)
BrierSimus12_True <- BrierSimus12_True + ggtitle(TeX('Level = $2,075$ ($\\kappa =1.2$)'))
BrierSimus12_True <-
  BrierSimus12_True + xlab("Outcome") + ylab("Prediction probability")
BrierSimus12_True <- BrierSimus12_True + theme(
  panel.grid.minor = element_blank(),
  text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18)
)
BrierSimus12_True <- BrierSimus12_True + ylim(0,1)
```


```{r pr.data12}
dis.thres12_MGPD <- sort(res_week3_12$Predict_Gumbel_12, decreasing = TRUE)
pr.data12_MGPD <-
  data.frame(DisThres = c(dis.thres12_MGPD),
             Model = rep("Gumbel", length(dis.thres12_MGPD)))

for (i in 1:length(dis.thres12_MGPD)) {
   pr.data12_MGPD$Precision[i] <- sum((res_week3_12$Outcome == 1) &
                                      (res_week3_12$Predict_Gumbel_12 > dis.thres12_MGPD[i]) , na.rm = T 
                                    ) / sum((res_week3_12$Predict_Gumbel_12 > dis.thres12_MGPD[i]) )
  pr.data12_MGPD$Recall[i] <- sum((res_week3_12$Outcome == 1) &
                                      (res_week3_12$Predict_Gumbel_12 > dis.thres12_MGPD[i]), na.rm = T 
                                    ) / sum( (res_week3_12$Outcome == 1))
}

dis.thres12_TRUE <- sort(res_week3_12$Predict_True_12, decreasing = TRUE)
pr.data12_TRUE <-
  data.frame(DisThres = c(dis.thres12_TRUE),
             Model = rep("True", length(dis.thres12_TRUE)))
for (i in 1:length(dis.thres12_TRUE)) {

     pr.data12_TRUE$Precision[i] <- sum((res_week3_12$Outcome == 1) &
                                      (res_week3_12$Predict_True_12 > dis.thres12_TRUE[i]) , na.rm = T 
                                    ) / sum((res_week3_12$Predict_True_12 > dis.thres12_TRUE[i]) )
  pr.data12_TRUE$Recall[i] <- sum((res_week3_12$Outcome == 1) &
                                      (res_week3_12$Predict_True_12 > dis.thres12_TRUE[i]), na.rm = T 
                                    ) / sum( (res_week3_12$Outcome == 1))
}

pr.data12 <- rbind(pr.data12_MGPD, pr.data12_TRUE)
```

```{r  PRCSimus_12}
PRCSimus_12 <-
  ggplot(data = pr.data12, aes(
    x = Recall,
    y = Precision,
    colour = Model,
    linetype = Model
  )) + geom_path()
PRCSimus_12 <- PRCSimus_12 + geom_hline(yintercept = sum( (res_week3_12$Outcome == 1))/length(res_week3_12$Outcome))
PRCSimus_12 <- PRCSimus_12 + xlim(c(0, 1)) + ylim(c(0, 1))
PRCSimus_12 <- PRCSimus_12 + scale_color_manual(values = c("blue", "orange"))
PRCSimus_12 <- PRCSimus_12 + xlab("Recall") + ylab("Precision")
PRCSimus_12 <- PRCSimus_12 + ggtitle(TeX('Level = $2,075$ ($\\kappa =1.2$)'))
PRCSimus_12 <- PRCSimus_12 + theme(
  panel.grid.minor = element_blank(),
 text = element_text(size = 16),
  axis.text.x = element_text(size = 14),
  axis.text.y = element_text(size = 14),
  plot.title = element_text(size = 18),
  legend.title=element_text(size=12), 
  legend.text=element_text(size=12)
)
PRCSimus_12
```


## Table 7a)
### Standardized Brier scores 
```{r brier scores}
##0.5
p_05 <- mean(res_week3_05$Outcome)
brier_gumbel_05 <-
  1 - mean((res_week3_05$Predict_Gumbel_05 - res_week3_05$Outcome) ^ 2) /
  (p_05 * (1 - p_05))
brier_logit_05 <-
  1 - mean((res_week3_05$Predict_Logit_05 - res_week3_05$Outcome) ^ 2,
           na.rm = T) /
 (p_05 * (1 - p_05))
brier_true_05 <-
  1 - mean((res_week3_05$Predict_True_05 - res_week3_05$Outcome) ^ 2,
           na.rm = T) /
   (p_05 * (1 - p_05))

##0.75
p_075 <- mean(res_week3_075$Outcome)
brier_gumbel_075 <-
  1 - mean((res_week3_075$Predict_Gumbel_075 - res_week3_075$Outcome) ^ 2) /
   (p_075 * (1 - p_075))
brier_logit_075 <-
  1 - mean((res_week3_075$Predict_Logit_075 - res_week3_075$Outcome) ^ 2,
           na.rm = T) /
 (p_075 * (1 - p_075))
brier_true_075 <-
  1 - mean((res_week3_075$Predict_True_075 - res_week3_075$Outcome) ^ 2,
           na.rm = T) /
(p_075 * (1 - p_075))


##0.95
p_095 <- mean(res_week3_095$Outcome)
brier_gumbel_095 <-
  1 - mean((res_week3_095$Predict_Gumbel_095 - res_week3_095$Outcome) ^ 2) /
  (p_095 * (1 - p_095))
brier_true_095 <-
  1 - mean((res_week3_095$Predict_True_095 - res_week3_095$Outcome) ^ 2,
           na.rm = T) /
(p_095 * (1 - p_095))

##1
p_1 <- mean(res_week3_1$Outcome)
brier_gumbel_1 <-
  1 - mean((res_week3_1$Predict_Gumbel_1 - res_week3_1$Outcome) ^ 2) /
  (p_1 * (1 - p_1))
brier_true_1 <-
  1 - mean((res_week3_1$Predict_True_1 - res_week3_1$Outcome) ^ 2) /
   (p_1 * (1 - p_1))

##1.2
p_12 <- mean(res_week3_12$Outcome)
brier_gumbel_12 <-
  1 - mean((res_week3_12$Predict_Gumbel_12 - res_week3_12$Outcome) ^ 2) /
  (p_12 * (1 - p_12))
brier_true_12 <-
  1 - mean((res_week3_12$Predict_True_12 - res_week3_12$Outcome) ^ 2) /
  (p_12 * (1 - p_12))
```

```{r table7aBrier}
table7aBrier <- data.frame(matrix(c(brier_gumbel_05, brier_gumbel_075, brier_gumbel_095, brier_gumbel_1, brier_gumbel_12, brier_logit_05, brier_logit_075, NA, NA, NA,brier_true_05, brier_true_075, brier_true_095, brier_true_1, brier_true_12), byrow = T, ncol = 5))
rownames(table7aBrier) <- c( "GP", "Logistic", "True")
colnames(table7aBrier) <-c(0.5, 0.75, 0.95, 1, 1.2)
kable(table7aBrier)
```

### Table of Average Precision Score ###
```{r APS}
##  0.5 ###
AP_GP_05 <- sum(pr.data05_MGPD$Precision*(pr.data05_MGPD$Recall - c(0,pr.data05_MGPD$Recall[-length(dis.thres05_MGPD)])), na.rm = T)
AP_LOGIT_05 <- sum(pr.data05_LOGIT$Precision*(pr.data05_LOGIT$Recall - c(0,pr.data05_LOGIT$Recall[-length(dis.thres05_LOGIT)])), na.rm = T)
AP_TRUE_05 <- sum(pr.data05_TRUE$Precision*(pr.data05_TRUE$Recall - c(0,pr.data05_TRUE$Recall[-length(dis.thres05_TRUE)])), na.rm = T)


##  0.75 ###
AP_GP_075 <- sum(pr.data075_MGPD$Precision*(pr.data075_MGPD$Recall - c(0,pr.data075_MGPD$Recall[-length(dis.thres075_MGPD)])), na.rm = T)
AP_LOGIT_075 <- sum(pr.data075_LOGIT$Precision*(pr.data075_LOGIT$Recall - c(0,pr.data075_LOGIT$Recall[-length(dis.thres075_LOGIT)])), na.rm = T)
AP_TRUE_075 <- sum(pr.data075_TRUE$Precision*(pr.data075_TRUE$Recall - c(0,pr.data075_TRUE$Recall[-length(dis.thres075_TRUE)])), na.rm = T)

##  0.95 ###
AP_GP_095 <- sum(pr.data095_MGPD$Precision*(pr.data095_MGPD$Recall - c(0,pr.data095_MGPD$Recall[-length(dis.thres095_MGPD)])), na.rm = T)
AP_TRUE_095 <- sum(pr.data095_TRUE$Precision*(pr.data095_TRUE$Recall - c(0,pr.data095_TRUE$Recall[-length(dis.thres095_TRUE)])), na.rm = T)

## 1 ###
AP_GP_1 <- sum(pr.data1_MGPD$Precision*(pr.data1_MGPD$Recall - c(0,pr.data1_MGPD$Recall[-length(dis.thres1_MGPD)])), na.rm = T)
AP_TRUE_1 <- sum(pr.data1_TRUE$Precision*(pr.data1_TRUE$Recall - c(0,pr.data1_TRUE$Recall[-length(dis.thres1_TRUE)])), na.rm = T)

## 1.2 ###
AP_GP_12 <- sum(pr.data12_MGPD$Precision*(pr.data12_MGPD$Recall - c(0,pr.data12_MGPD$Recall[-length(dis.thres12_MGPD)])), na.rm = T)
AP_TRUE_12 <- sum(pr.data12_TRUE$Precision*(pr.data12_TRUE$Recall - c(0,pr.data12_TRUE$Recall[-length(dis.thres12_TRUE)])), na.rm = T)


```

```{r table7aAps}
table7aAps <- data.frame(matrix(c(AP_GP_05, AP_GP_075, AP_GP_095, AP_GP_1, AP_GP_12, AP_LOGIT_05, AP_LOGIT_075, NA, NA, NA,AP_TRUE_05, AP_TRUE_075, AP_TRUE_095, AP_TRUE_1, AP_TRUE_12), byrow = T, ncol = 5)) 
rownames(table7aAps) <- c( "GP", "Logistic", "True") 
colnames(tabl7aAps) <- c(0.5, 0.75, 0.95, 1, 1.2) 
kable(table7aAps)
```


